Probabilistic Catalogs for Crowded Stellar Fields

### 2012-10-31 paper/ms.tex
More writing

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{Figures/summaries.eps}
\end{center}
\caption{Summary images for test case 2.\label{fig:summaries}}
\end{figure}

\section{Comparison to SExtractor}

\begin{figure}
\begin{center}
\includegraphics[scale=0.45]{Figures/sex_N.eps}
\end{center}
\caption{The number of stars in the catalogs produced by \sex.\label{fig:sex_N}}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.45]{Figures/sex_inference.eps}
\end{center}
\caption{Inference of the luminosity function parameters using the $\sigma=0.5$
catalog from \sex.\label{fig:sex_inference}}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{Figures/summaries.eps}
\end{center}
\caption{Summary images for test case 2. The left panel shows the posterior
mean high-resolution scene. The middle panel shows the posterior mean scene
when observed at the resolution of the data, and the right hand panel shows the
model residuals.
\label{fig:summaries}}
\end{figure}

\section{Comparison to SExtractor}
In the previous section we established that the inference of the catalogs from
the data is computationally feasible and that the number of stars and the
luminosity function can be inferred from the image data, albeit with moderate
uncertainty. We now compare this approach with the output from the standard
tool \sex. To achieve this, we executed \sex~on the two test cases, for various
values of the significance level cutoff. This results in a set of catalogs
for each image, with more conservative cutoffs resulting in less stars detected
as compared to more agressive cutoffs. The results for the number of stars in
the images are shown in Figure~\ref{fig:sex_N}. The main result is that
\sex~significantly underestimates the number of stars in the image for all
possible values of the cutoff parameter.

\begin{figure}
\begin{center}
\includegraphics[scale=0.45]{Figures/sex_N.eps}
\end{center}
\caption{The number of stars in the catalogs produced by \sex. The true numbers
of stars shown in these plots are$\sim$82\% of the values listed in
Figure~\ref{tab:truth} because here we only count those stars with positions
in $[-1, 1] \times [-1, 1]$.
\label{fig:sex_N}}
\end{figure}

For Test Case 2, we then took the catalog produced by \sex~for the $0.5\sigma$
cutoff and fitted a broken power-law model to the list of fluxes in the catalog.
The results of this inference are shown in Figure~\ref{fig:sex_inference}.
The inference spuriously rules out the true values of the parameters. This
occurs because the uncertainty in the stellar fluxes is not propagated through
to the inference of the luminosity function.

\begin{figure}
\begin{center}
\includegraphics[scale=0.45]{Figures/sex_inference.eps}
\end{center}
\caption{Inference of the luminosity function parameters using the $0.5\sigma$
catalog from \sex.\label{fig:sex_inference}}
\end{figure}
